The Galaxy Cluster Merger Catalog: An Online Repository of Mock Observations from Simulated Galaxy Cluster Mergers

### 2016-09-13 paper/ms.tex
Couple more acks

\acknowledgements
JAZ thanks Eric Mandel for tips on using JS9 and for critical bug fixes and enhancements that were provided to make it work with the data in the catalog. JAZ acknowledges support through Chandra Award Number G04-15088X issued by the Chandra X-ray Center, which is operated by the Smithsonian Astrophysical Observatory for and on behalf of NASA under contract NAS8-03060.
KK was funded in part by the Gordon and Betty Moore Foundation's Data-Driven Discovery Initiative through Grant GBMF4561.

>>>>

\acknowledgements
The authors thank Eric Mandel (CfA) for tips on using JS9 and for critical bug fixes and enhancements that were provided to make it work with the data in the catalog, and Joseph DePasquale (CfA) for generating the home page image. JAZ acknowledges support through Chandra Award Number G04-15088X issued by the Chandra X-ray Center, which is operated by the Smithsonian Astrophysical Observatory for and on behalf of NASA under contract NAS8-03060. KK was funded in part by the Gordon and Betty Moore Foundation's Data-Driven Discovery Initiative through Grant GBMF4561.
